### 2017-11-30 README.Rmd
added running instruction
added method plotting
add travis badge
update readme

# dynalysis

@@

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("Zouter/dynalysis")
```

>>>>

# An evaluation framework for trajectory inference methods

![travis](https://travis-ci.com/Zouter/dynalysis.svg?token=pzNqJjk3yapU1Hk7sDg8&branch=master)

![overview](analysis/figures/toy_method_plots/grid.png)

@@

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("Zouter/dynalysis", dependencies = TRUE, upgrade_dependencies = TRUE)
```

### Running

To run locally, install `docker` and run `docker build -t dynalysis .`
